---
title: "Bots Detection"
#author: "Song Wang"
date: "6/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)

library(tidyverse) #include ggplot2, dyplyr, readr, tydyr
#library(dygraphs) # dynamic graph
library(xts)
library(Matrix)
theme_update(plot.title = element_text(hjust = 0.5))
source("function.R")
```

```{r loading data}
#load("../report/2017-05-27/report_0601.RData")
load("../report/2017-05-27/report_0626.RData")
followers <- subset(followers, !is.na(cluster))
# followers$clust_cat <- addNA(followers$clust_cat)
# levels(followers$clust_cat)[9] <- "NA"
table(followers$clust_cat)
table(followers$period)
```


## Part I: Using Pagerank to detect bots.
PageRank was developed to evaluate the importance of web-pages via the link structures. More generally, it can used as a centrality measures of nodes in various networks. 

Here we hypothsize that bots have fewer followers and thus lower pagerank scores. A benefits that pagerank has is that it is difficult for bots to adjust themselves to change the scores. 

We calculate the pagerank scores of each Trump followers, use the verified account as non-bots accounts to see whether there is differences for this scores.

Two pagerank scores presented here

1.Pagerank1 from the network among **377725** followers themseleves.

* Network statistics: 377725 nodes, 20766474 edges, mean degree = 54.98.
   **65.8%** have zero out degree(following nobody); **18.2%** have zero in degree; **12.6%** have zero degrees

* Page rank actually don't work well!  -- not able to ditinguish verified account and regular accounts

2. Pagerank2 from the symmetrized bipartite graph between followers and people they are following (>=10).

* Network statistics: (considered as bipartite graph) 324933 x 9118691, total edges: 525,894,470.
5080581 out 9,118,691 have at least 10 followers in each stage. 9,118,691 have 10 followers among all the sample of 377725(324933).

* no zero degrees. 1190/324933/377725 having <10 friends (out degree); min in degree is 10

* Page rank has more very low scores (1e-7 (~12%, ~2%), 1e-6.5 (37%, 15%)). See the plot below.




```{r}
p0 <- followers %>% group_by(period, clust_cat) %>% summarise(count = n()) %>% 
  ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral") +xlab("")+ggtitle("full data")
```


### Two pageranks


**pagerank 1 (w/o personalization)**

```{r}
p11 <- followers %>% ggplot(aes(x = log10(pg1))) + stat_ecdf(geom="step", aes(group = verified, color = verified )) +labs(x= "pagerank (in log10)", y = "cumulative probability") + ggtitle("pagerank1")

p12 <- followers %>% ggplot(aes(x = log10(pg1_personalized))) + stat_ecdf(geom="step",aes(group = verified, color = verified )) +  labs(x= "pagerank (in log10)", y = "cumulative probability") + ggtitle("pagerank1 personalized")

multiplot(p11, p12,  cols = 2)

# p12 <- ggplot(dat, aes(logpg1, ..density..))+
#   geom_histogram(aes(color=verified,  group = verified),  bins =100, position = "stack")+
#   labs(x= "pagerank (in log10)")
# p13 <- ggplot(dat, aes(logpg1, color=verified, fill = verified ))+
#   geom_density(aes(  group = verified), alpha =0.1,   position = "stack")+ labs(x= "pagerank (in log10)")
# multiplot(p11, p12, p13,  cols = 2)
```


```{r}
p11_1 <- followers %>% ggplot(aes(x = log10(pg1_core3))) + stat_ecdf(geom="step",aes(group = verified, color = verified )) +  labs(x= "pagerank (in log10)", y = "cumulative probability") + ggtitle("pagerank1 on 3-core")

p12_1 <- followers %>% ggplot(aes(x = log10(pg1_p_core3))) + stat_ecdf(geom="step",aes(group = verified, color = verified )) +  labs(x= "pagerank (in log10)", y = "cumulative probability") + ggtitle("pagerank1 personalized on 3-core")
multiplot(p11_1, p12_1,  cols = 2)
```

**pagerank 2 (w/o personalization)**


```{r}
p21 <- followers %>% ggplot(aes(x = log10(pg2))) + stat_ecdf(geom="step",aes(group = verified, color = verified )) + labs(x= "pagerank (in log10)", y = "cumulative probability")+ ggtitle("pagerank2")

p22 <- followers %>% ggplot(aes(x = log10(pg2_personalized))) + stat_ecdf(geom="step",aes(group = verified, color = verified )) +  labs(x= "pagerank (in log10)", y = "cumulative probability") + ggtitle("pagerank2 personalized")
multiplot(p21, p22, cols = 2) 
```




Next, the plots above indicates (espcially for pagerank1), verified account tend to have high scores. Bots tend to have lower scores, let's look at the followers with lowest **5%** of the scores (```X <= quantile(X, 0.05, na.rm = T)+1e-10)```). 
```{r}
#68727 taking minimum values, using 1e-10 breaking 
p31 <- followers %>% subset( pg1 <= (quantile(pg1, 0.05, na.rm = T)+1e-10)) %>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")+ggtitle("tail of pg1")


p31_1 <- followers %>% subset(pg1_personalized <= quantile(pg1_personalized, 0.05, na.rm = T)+1e-10) %>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral") +ggtitle(paste0("tail of pg1_personalized"))


p32 <- subset(followers, pg2 <= quantile(pg2, 0.05, na.rm = T)+1e-10)%>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")+ggtitle("tail of pg2")


p32_1 <- subset(followers, pg2_personalized <= quantile(pg2_personalized, 0.05, na.rm = T)+1e-10)%>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")+ggtitle("tail of pg2_personalized")


p33 <- followers %>% 
  subset(pg1_core3 <= quantile(pg1_core3, 0.05, na.rm = T)+1e-10)%>% 
  group_by(period, clust_cat) %>% summarise(count = n()) %>% 
  ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral") + ggtitle("tail of pagerank_core3")

p33_1 <- followers %>% 
  subset(pg1_p_core3 <= quantile(pg1_p_core3, 0.05, na.rm = T)+1e-10)%>% 
  group_by(period, clust_cat) %>% summarise(count = n()) %>% 
  ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral") + ggtitle("tail of pagerank_p_core3")


p34 <- subset(followers,followers_count <= quantile(followers_count, 0.05, na.rm = T)+1e-10)%>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")+ggtitle("tail of followers_count")

p35 <- followers %>% 
  mutate(followers_following = log10((followers_count+1)/(1+friends_count)))%>%
  subset(followers_following <= quantile(followers_following, 0.05, na.rm = T)+1e-10)%>% 
  group_by(period, clust_cat) %>% summarise(count = n()) %>% 
  ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")+ ggtitle("tail of followers_counts friends_counts ratio")

p36 <- followers %>% 
    mutate(retweet_total = RT_only+ RT_comments)%>%
    subset(retweet_total >= quantile(retweet_total, 0.95, na.rm = T)+1e-10)%>% 
  group_by(period, clust_cat) %>% summarise(count = n()) %>% 
  ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")+ ggtitle("Right tail of retweet count total")

```

**The tails part of pagerank1, pagerank2, etc **


```{r tail part of PageRanks}

# pdf("tail_bots.pdf", onefile = TRUE)

multiplot(p0, p31, cols = 2)

multiplot(p0, p31_1, cols = 2)

multiplot(p0, p32, cols = 2)

multiplot(p0, p32_1, cols = 2)

multiplot(p0, p33, cols = 2)

multiplot(p0, p33_1, cols = 2)

multiplot(p0, p34, cols = 2)

multiplot(p0, p35, cols = 2)

multiplot(p0, p36, cols = 2)

#dev.off()
```

```{r}
cor_mat <- cor(followers[,c("followers_count", "friends_count", "count_mean_timeline",'pg1', 'pg1_personalized','pg2', 'pg2_personalized','pg1_core3', "pg1_p_core3")], use = 'pairwise.complete.obs')
cor_mat[row(cor_mat)<col(cor_mat)] <- 0
balloon.plot(round(as.matrix(cor_mat),3), text = T, xlabel = colnames(cor_mat), ylabel = rownames(cor_mat))+ggtitle("Correlation among various criteria")

```
Findings: 

1. Various PageRanks are strongly correlated with each other. And it is correlated with followers count or friends count. 

2. While daily_tweets frequency is not so much correlated with other critieria.

3. pg1, pg1_personalized etc. are similary. PageRanks is a kind of centrality measure.



**PageRank Scores within each clusters**


```{r}
followers  %>% ggplot(aes(log10(pg1))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  facet_grid(.~period) +
  labs(y = "cumulative probability")+labs(title = "pagerank1")

followers  %>% ggplot(aes(log10(pg1_core3))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat)) + 
  facet_grid(.~period) +
  labs(y = "cumulative probability")+labs(title = "pagerank1 on 3-core")

followers  %>% ggplot(aes(log10(pg2))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
    facet_grid(.~period) +
  labs(y = "cumulative probability")+labs(title = "pagerank2")

followers  %>% ggplot(aes(log10(pg1_personalized))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  facet_grid(.~period) +
  labs(y = "cumulative probability")+labs(title = "pagerank1 personalized")

followers  %>% ggplot(aes(log10(pg1_p_core3))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  facet_grid(.~period) +    
  labs(y = "cumulative probability")+labs(title = "pagerank1 personalized on 3-core")

followers  %>% ggplot(aes(log10(pg2_personalized))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  facet_grid(.~period) +
  labs(y = "cumulative probability")+labs(title = "pagerank2 personalized")

```
**pg1, pg1_personalized**



```{r}
followers  %>% ggplot(aes(log10(pg1))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "pagerank1")

followers  %>% ggplot(aes(log10(pg1_core3))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "pagerank1 on 3-core")

followers  %>% ggplot(aes(log10(pg2))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "pagerank2")

followers  %>% ggplot(aes(log10(pg1_personalized))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "pagerank1 personalized")

followers  %>% ggplot(aes(log10(pg1_p_core3))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "pagerank1 personalized on 3-core")

followers  %>% ggplot(aes(log10(pg2_personalized))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "pagerank2 personalized")

```


```{r}
followers  %>% ggplot(aes(log10(followers_count))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "follower count")

followers  %>% ggplot(aes(log10(count_mean_timeline))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+labs(title = "daily retweeting frequency")

```

## Next Step ?






