---
title: "Trump Twitter Followers"
author: "Song Wang"
date: "May 31, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list =ls())

library(tidyverse) #include ggplot2, dyplyr, readr, tydyr
library(dygraphs) # dynamic graph
library(xts)
library(Matrix)

```


```{r process data, include=FALSE, eval=FALSE}
#Read in followers
followers <- read.csv("../results_following/followers_with_cluster_info.csv", colClasses = c("character"))

#correct variable types
#factor
followers$cluster <- as.factor(as.numeric(followers$cluster))
#data time
#followers$created_at <- as.POSIXct(followers$created_at, format = "%a %b %d %H:%M:%S %z %Y")
followers$created_at <- as.POSIXct(followers$created_at)
followers$first_date_timeline <- as.Date(followers$first_date_timeline)
followers$last_date_timeline <- as.Date(followers$last_date_timeline)
#non-numerical
non_numerical_cols <- c("period","cluster", "clust_label","clust_cat","id_str", "screen_name", 
                        "name",  "description","created_at", "lang",
                        "location", "time_zone", "verified", "first_date_timeline","last_date_timeline")
non_numerical_ids <- match(non_numerical_cols, names(followers))
for( i in 1:ncol(followers)){
  if (!(i %in% non_numerical_ids)){
    followers[,i] <- as.numeric(followers[,i]) 
  }
}
rm(non_numerical_cols,non_numerical_ids)


#reorder
tmp <- unique(followers$clust_cat)
new_levels <- c("Trump supporters","conservatives","anti-feminist conservatives","liberals","news&regional",
               "international","non-political", "other countries")
followers$clust_cat <- as.factor(match(followers$clust_cat, new_levels))
followers$clust_cat <- factor(followers$clust_cat, levels = 1:length(new_levels), labels = new_levels)  # 1:7
table(followers$clust_cat)


tmp <- unique(followers$period)
new_levels <- c("before announcement",  "before primary",   "before election" ); match(tmp, new_levels)
followers$period <- as.factor(match(followers$period, new_levels))
followers$period <- factor(followers$period, 1:3, new_levels)
table(followers$period)

save(followers, file ="../report/2017-05-27/report_0612.RData")

```


## Introduction
first version May 31, 2017
updated on Jun 1, Jun 12




## Part I: Using Pagerank to detect bots.
PageRank was developed to evaluate the importance of web-pages via the link structures. More generally, it can used as a centrality measures of nodes in various networks. 

Here we hypothsize that bots have fewer followers and thus lower pagerank scores. A benefits that pagerank has is that it is difficult for bots to adjust themselves to change the scores. 

We calculate the pagerank scores of each Trump followers, use the verified account as non-bots accounts to see whether there is differences for this scores.

Two pagerank scores presented here

1.Pagerank1 from the network among 377725 followers themseleves.

* Network statistics: 377725 nodes, 20766474 edges, mean degree = 54.98.
   **65.8%** have zero out degree(following nobody); **18.2%** have zero in degree; **12.6%** have zero degrees

* Page rank actually don't work well!  -- not able to ditinguish verified account and regular accounts

2. Pagerank2 from the symmetrized bipartite graph between followers and people they are following (>=10).

* Network statistics: (considered as bipartite graph) 324933 x 9118691, total edges: 525,894,470.
5080581 out 9,118,691 have at least 10 followers in each stage. 9,118,691 have 10 followers among all the sample of 377725(324933).

* no zero degrees. 1190/324933/377725 having <10 friends (out degree); min in degree is 10

* Page rank has more very low scores (1e-7 (~12%, ~2%), 1e-6.5 (37%, 15%)). See the plot below.

```{r loading data, echo =FALSE }
#load("../report/2017-05-27/report_0601.RData")
load("../report/2017-05-27/report_0612.RData")
followers$clust_cat <- addNA(followers$clust_cat)
levels(followers$clust_cat)[9] <- "NA"
source("function.R")
```


```{r echo=FALSE,  message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
p0 <- followers %>% group_by(period, clust_cat) %>% summarise(count = n()) %>% 
  ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral") +xlab("")
```


### Two pageranks

```{r pagerank1, echo =FALSE, warning=FALSE, fig.width=8, fig.height=6}
## some analysis on the page ranks w.r.t. verified account.
#G <- graph_from_edgelist(el,directed = T)
#pg <- page_rank(G)
library(tidyverse)
dat <- followers[,c("screen_name", "verified",'pg1','pg2','pg1_personalized', 'pg2_personalized')]
dat <- dat%>%mutate(logpg1 = log10(pg1)) %>% mutate(logpg2 = log10(pg2)) %>% 
  mutate(logpg1_personalized = log10(pg1_personalized))%>%
  mutate(logpg2_personalized = log10(pg2_personalized))
dat$verified <- as.factor(dat$verified)
```

**pagerank 1 (w/o personalization)**

```{r, echo =FALSE, warning=FALSE, fig.width=8, fig.height=6}
p11 <- ggplot(dat, aes(logpg1)) + stat_ecdf(geom="step",aes(group = verified, color = verified )) + 
  labs(x= "pagerank (in log10)", y = "cumulative probability")
p12 <- ggplot(dat, aes(logpg1, ..density..))+
  geom_histogram(aes(color=verified,  group = verified),  bins =100, position = "stack")+
  labs(x= "pagerank (in log10)")
p13 <- ggplot(dat, aes(logpg1, color=verified, fill = verified ))+
  geom_density(aes(  group = verified), alpha =0.1,   position = "stack")+ labs(x= "pagerank (in log10)")

multiplot(p11, p12, p13,  cols = 2)
```




```{r, echo =FALSE, warning=FALSE, fig.width=8, fig.height=6}
p11_1 <- ggplot(dat, aes(logpg1_personalized)) + stat_ecdf(geom="step",aes(group = verified, color = verified )) + 
  labs(x= "pagerank (in log10)", y = "cumulative probability")
p12_1<- ggplot(dat, aes(logpg1_personalized, ..density..))+
  geom_histogram(aes(color=verified,  group = verified),  bins =100, position = "stack")+
  labs(x= "pagerank (in log10)")
p13_1 <- ggplot(dat, aes(logpg1_personalized, color=verified, fill = verified ))+
  geom_density(aes(  group = verified), alpha =0.1,   position = "stack")+
  labs(x= "pagerank (in log10)")
multiplot(p11_1, p12_1, p13_1,  cols = 2)
```


**pagerank 2 (w/o personalization)**

```{r, echo =FALSE, warning=FALSE, fig.width=8, fig.height=6}
p21 <- ggplot(dat, aes(logpg2)) + stat_ecdf(geom="step",aes(group = verified, color = verified )) + 
  labs(x= "pagerank (in log10)", y = "cumulative probability")
p22 <- ggplot(dat, aes(logpg2, ..density..))+
  geom_histogram(aes(color=verified,  group = verified), bins =100, position = "stack")+
  labs(x= "pagerank (in log10)")
p23 <- ggplot(dat, aes(logpg2, color=verified, fill = verified ))+
  geom_density(aes(  group = verified), alpha =0.1, position = "stack")+
  labs(x= "pagerank (in log10)")

multiplot(p21, p22, p23, cols = 2) 
```


```{r, echo =FALSE, warning=FALSE, fig.width=8, fig.height=6}
p21_1 <- ggplot(dat, aes(logpg2_personalized)) + stat_ecdf(geom="step",aes(group = verified, color = verified )) + 
  labs(x= "pagerank (in log10)", y = "cumulative probability")
p22_1 <- ggplot(dat, aes(logpg2_personalized, ..density..))+
  geom_histogram(aes(color=verified,  group = verified), bins =100, position = "stack")+
  labs(x= "pagerank (in log10)")
p23_1 <- ggplot(dat, aes(logpg2_personalized, color=verified, fill = verified ))+
  geom_density(aes(  group = verified), alpha =0.1, position = "stack")+
  labs(x= "pagerank (in log10)")

multiplot(p21_1, p22_1, p23_1, cols = 2) 
```

Next, the plots above indicates (espcially for pagerank1), verified account tend to have high scores. Bots tend to have lower scores, let's look at the followers with lowest 25% of the scores. 

```{r,  echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
#68727 minimum values
p31 <- subset(followers, pg1 < quantile(pg1,0.25, na.rm = T)) %>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")
p32 <- subset(followers, pg2 < quantile(pg2,0.25, na.rm = T))%>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")
p33 <- subset(followers,followers_count < quantile(followers_count, 0.25, na.rm = T))%>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")

p34 <- followers %>% mutate(followers_following = log10(followers_count+1)/log10(1+friends_count))%>%
subset(followers_following < quantile(followers_following, 0.25, na.rm = T))%>% group_by(period, clust_cat) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = clust_cat, label = clust_cat)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")
```


```{r tail part of pg1, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
multiplot(p0, p31, cols = 1)
```

**The tail part of pagerank1 **


```{r tail part of pg2, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
multiplot(p0, p32, cols = 1)
```

**The tail part of pagerank2**

```{r,  echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
multiplot(p33,p34, cols = 1)
```

**Performance of using the tail part of followers_count, followers_count/friends_count**

```{r,  echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
followers  %>% ggplot(aes(log10(pg1))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")

followers  %>% ggplot(aes(log10(pg2))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")

followers  %>% ggplot(aes(log10(pg1_personalized))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")

followers  %>% ggplot(aes(log10(pg2_personalized))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")

```

##Part II verifying the clsutering

In this part, I did the following things:

1. visualize the similarity among 50 clusters in each of the three stages (clusters are ordered based on the category names)

2. explore [sparseAHC](https://github.com/khabbazian/sparseAHC), algorithm doing clustering based on the similarity graph. This is trying to verified 1, the performance of the algorithms; 2, justify that the combining the 50 clusters into 8 categories is valid.

3. the results: 
  + the overlapping between sparseAHC and manually combined labels is low.
  + the balloon plot show that the similarity among Trump supporters are realatively high.
  
  
```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6, eval=FALSE }
#some exploratory on 
load("../results_following/result3/analysis.RData")
Z <- membershipM(km_row$cluster)
NZ <-Z%*% Diagonal(dim(Z)[2],km_row$size^(-1))
S1 <- t(NZ) %*% L%*%t(L)%*% NZ

load("../results_following/result2/analysis.RData")
Z <- membershipM(km_row$cluster)
NZ <-Z%*% Diagonal(dim(Z)[2],km_row$size^(-1))
S2 <- t(NZ) %*% L%*%t(L)%*% NZ


load("../results_following/result1/analysis.RData")
Z <- membershipM(km_row$cluster)
NZ <-Z%*% Diagonal(dim(Z)[2],km_row$size^(-1))
S3 <- t(NZ) %*% L%*%t(L)%*% NZ

save(S1,S2,S3, file = "similarity50.RData")
```


```{r}
load("similarity50.RData")
cluster_info <- read.csv("../results_following/cluster_summary.csv")
cluster_info <- cluster_info[1:50,]
#cat_names <- unique(cluster_info$clust_cat)
cat_names <-c("Trump supporters","conservatives","anti-feminist conservatives","liberals","news&regional",
              "international","non-political", "other countries")
ord <- NULL
for( nn in cat_names){
  ord <- c(ord, which(cluster_info$clust_cat == nn))
}

  
heatmap(as.matrix(S1),main = "using original cluster id")

library(sparseAHC)
hclust = sparseAHC(S1, linkage = "average")
plot(hclust)
nclust = 10
clus = cutree(hclust, nclust )
for( i in 1:nclust ){
  cat("i=",i,"\t", cluster_info$cluster_label[which(clus ==i)], "\n")
}

image(S1) 

S1_sorted <- S1[ord, ord]
table( match(cluster_info$clust_cat, cat_names))
# 1  2  3  4  5  6  7  8 
# 4  6  2  6  1  2 14 15
ii <- cumsum(table( match(cluster_info$clust_cat, cat_names)))
balloon.plot(round(S1_sorted*10^4,4),text = F, xlabel = ord, ylabel = ord)+
  geom_abline(slope =0, intercept = 50-ii[1]+1, color = "red") +
  geom_vline(xintercept=ii[1], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[2]+1, color = "red") +
  geom_vline(xintercept=ii[2], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[3]+1, color = "red") +
  geom_vline(xintercept=ii[3], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[4]+1, color = "red") +
  geom_vline(xintercept=ii[4], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[5]+1, color = "red") +
  geom_vline(xintercept=ii[5], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[6]+1, color = "red") +
  geom_vline(xintercept=ii[6], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[7]+1, color = "red") +
  geom_vline(xintercept=ii[7], color ="red")+
  scale_size(range = c(0, 4))+ labs(title = "similariy among clusters (in 1e-4)")


```

## before primary

```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
#some exploratory on 
cluster_info <- read.csv("../results_following/cluster_summary.csv")
cluster_info <- cluster_info[51:100,]
#cat_names <- unique(cluster_info$clust_cat)
cat_names <-c("Trump supporters","conservatives","anti-feminist conservatives","liberals","news&regional",
              "international","non-political", "other countries")
ord <- NULL
for( nn in cat_names){
  ord <- c(ord, which(cluster_info$clust_cat == nn))
}

S2_sorted <- S2[ord, ord]
heatmap(as.matrix(S2),main = "using original cluster id")
library(sparseAHC)
hclust = sparseAHC(S2, linkage = "average")
plot(hclust)
nclust = 10
clus = cutree(hclust, nclust )
for( i in 1:nclust ){
  cat("i=",i,"\t", cluster_info$cluster_label[which(clus ==i)], "\n")
}

image(S2)

table( match(cluster_info$clust_cat, cat_names))
# 1  2  3  4  5  6  7  8 
# 4  6  2  6  1  2 14 15
ii <- cumsum(table( match(cluster_info$clust_cat, cat_names)))
balloon.plot(round(S2_sorted*10^4,4),text = F, xlabel = ord, ylabel = ord)+
  geom_abline(slope =0, intercept = 50-ii[1]+1, color = "red") +
  geom_vline(xintercept=ii[1], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[2]+1, color = "red") +
  geom_vline(xintercept=ii[2], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[3]+1, color = "red") +
  geom_vline(xintercept=ii[3], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[4]+1, color = "red") +
  geom_vline(xintercept=ii[4], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[5]+1, color = "red") +
  geom_vline(xintercept=ii[5], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[6]+1, color = "red") +
  geom_vline(xintercept=ii[6], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[7]+1, color = "red") +
  geom_vline(xintercept=ii[7], color ="red")+
  scale_size(range = c(0, 4)) + labs(title = "similariy among clusters (in 1e-4)")




```

## before election

```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
#some exploratory on 
cluster_info <- read.csv("../results_following/cluster_summary.csv")
cluster_info <- cluster_info[101:150,]
#cat_names <- unique(cluster_info$clust_cat)
cat_names <-c("Trump supporters","conservatives","anti-feminist conservatives","liberals","news&regional",
              "international","non-political", "other countries")
ord <- NULL
for( nn in cat_names){
  ord <- c(ord, which(cluster_info$clust_cat == nn))
}
S3_sorted <- S3[ord, ord]
heatmap(as.matrix(S3),main = "using original cluster id")
library(sparseAHC)
hclust = sparseAHC(S3, linkage = "average")
plot(hclust)
nclust = 10
clus = cutree(hclust, nclust )
for( i in 1:nclust ){
  cat("i=",i,"\t", cluster_info$cluster_label[which(clus ==i)], "\n")
}


image(S3)

table( match(cluster_info$clust_cat, cat_names))
# 1  2  3  4  5  6  7  8 
# 4  6  2  6  1  2 14 15
ii <- cumsum(table( match(cluster_info$clust_cat, cat_names)))
balloon.plot(round(S3_sorted*10^4,4),text = F, xlabel = ord, ylabel = ord)+
  geom_abline(slope =0, intercept = 50-ii[1]+1, color = "red") +
  geom_vline(xintercept=ii[1], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[2]+1, color = "red") +
  geom_vline(xintercept=ii[2], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[3]+1, color = "red") +
  geom_vline(xintercept=ii[3], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[4]+1, color = "red") +
  geom_vline(xintercept=ii[4], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[5]+1, color = "red") +
  geom_vline(xintercept=ii[5], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[6]+1, color = "red") +
  geom_vline(xintercept=ii[6], color ="red")+
  geom_abline(slope =0, intercept = 50-ii[7]+1, color = "red") +
  geom_vline(xintercept=ii[7], color ="red")+
  scale_size(range = c(0, 4))


```


## Some Validation about tweet counts

- Address potential issues, 3200 tweets, may not cover all the tweets, definitely not covered (10.5%), and (12.8%) we don't have their timeline -- due to privacy or no tweets.
```{r, eval=FALSE, echo=FALSE}
# clearly truncatation for total at 3200 
table((followers$first_date_timeline >as.Date('2015-06-16'))*(followers$count_total_timeline > 3200), followers$period)
sum((followers$first_date_timeline >as.Date('2015-06-16'))*(followers$count_total_timeline > 3200), na.rm = T)/nrow(followers)
sum(is.na(followers$first_date_timeline))/nrow(followers)
```

- Account started to following Trump at different time. Currently, constraint to 3 following stages, Trump followers always tweets more frequently.

```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
p91 <- followers  %>% ggplot(aes(log10(1+count_mean_timeline))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+facet_grid(period~.)
p91
```

```{r, fig.width=8, fig.height=6}
followers  %>% mutate(retweet_ajusted = log10(1+retweet_trump_count)/(log10(1+count_total_timeline))) %>%ggplot(aes(retweet_ajusted)) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")+facet_grid(period~.)
```

##Part III visualization of some variables.

```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
followers %>% mutate(log_daily_count = log10(1+count_mean_timeline)) %>% ggplot(aes(x = log_daily_count)) +
  geom_histogram(stat = "bin",  binwidth = 0.05) +labs(x = "average daily tweets (in log10)")
                 


followers%>% mutate(log_total_count = log10(1+count_total_timeline)) %>% ggplot(aes(x = log_total_count)) +
  geom_histogram(stat = "bin",  binwidth = 0.1) +labs(x = "total tweets from timeline (in log10)")

followers %>% mutate(ndays = count_total_timeline/count_mean_timeline) %>%
  ggplot(aes(ndays)) + geom_histogram(aes(group= clust_cat, color= clust_cat), bins = 50, position = "stack")

p51 <- followers %>% mutate(ndays = count_total_timeline/count_mean_timeline) %>%
  ggplot(aes(ndays)) +stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")

p52 <-followers %>% mutate(ndays = count_total_timeline/count_mean_timeline) %>%
  ggplot(aes(ndays)) + geom_histogram(aes( color= clust_cat),binwidth = 30)+facet_grid(clust_cat~.)

p53<- followers %>% mutate(ndays = count_total_timeline/count_mean_timeline) %>%
  ggplot(aes(ndays))+
  geom_density(aes(color= clust_cat, fill = clust_cat), alpha =0.1,   position = "stack")+facet_grid(clust_cat~.)
p51
p52
p53
```


```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
p61 <- followers  %>% ggplot(aes(created_at)) +
  geom_density(aes(color= clust_cat, fill = clust_cat), alpha =0.1,   position = "stack")+facet_grid(clust_cat~.)

p62 <- followers  %>% subset(created_at > as.Date('2015-06-16')) %>%ggplot(aes(created_at)) +
  geom_density(aes(color= clust_cat, fill = clust_cat), alpha =0.1,   position = "stack")+facet_grid(clust_cat~.)
p61
p62
```

```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
p71 <- followers  %>% subset(created_at > as.Date('2015-06-16')) %>%ggplot(aes(log10(count_mean_timeline))) +
  geom_density(aes(color= clust_cat, fill = clust_cat), alpha =0.1,   position = "stack")+facet_grid(clust_cat~.)

p72 <- followers  %>% subset(created_at > as.Date('2015-06-16'))%>% ggplot(aes(log10(count_mean_timeline))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")
p71
p72
```

```{r, echo = FALSE, warning=FALSE, fig.width=8, fig.height=6}
p81 <- followers %>% ggplot(aes(log10(1+count_mean_timeline))) +
  geom_density(aes(color= clust_cat, fill = clust_cat), alpha =0.1,   position = "stack")+facet_grid(clust_cat~.)

p82 <- followers  %>% ggplot(aes(log10(1+count_mean_timeline))) +
  stat_ecdf(geom="step",aes(group= clust_cat, color= clust_cat )) + 
  labs(y = "cumulative probability")
p81
p82
```




