---
title: "A Study of Donald Trump's Twitter Followers"
author: Yini Zhang 
date: May 11, 2017
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(dygraphs)
library(xts)

```


# Section I: The Growth of Trump's Twitter Followers 

Data came from SMAD's Twitter archive collecting tweets through Twitter's streaming API. The archive contains 1% of random Twitter data. Data credit goes to J.

The timeframe is from 2015/01/01 to 2016/11/09.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}

#use created_at and rt.user.followers_count, remove rt.user.id that's not trump

df_by_minute = read.csv("Trump followers/Trump_followers_minute_by_minute.csv", header = TRUE, colClasses = c("character", "numeric", "numeric"))
df_by_minute$created_at = as.POSIXct(df_by_minute$created_at,format="%m/%d/%y %H:%M")
df_by_minute_simp = df_by_minute %>% group_by(created_at) %>% summarise(followers = mean(rt.user.followers_count)) %>% mutate(date = as.Date(created_at))

#by minute
dt1 = xts(df_by_minute_simp$followers, order.by = df_by_minute_simp$created_at)
dygraph(dt1,ylab="Volume", 
        main="Trump's Twitter follower counts by minute") %>%
  dyRangeSelector() %>% dyEvent("2015-6-16", "announced candidacy", labelLoc = "bottom") %>%
  dyEvent("2016-7-19", "became the nominee", labelLoc = "bottom") %>%
  dyEvent("2016-11-8", "won the election", labelLoc = "bottom")
```

**Figure 1: Trump's Twitter follower counts by minute**

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
#by day
temp = df_by_minute_simp %>% group_by(date) %>% summarise(ave_followers = mean(followers))
dt2 = xts(temp$ave_followers, order.by = temp$date)
dygraph(dt2,ylab="Volume", 
        main="Trump's Twitter follower counts by day") %>%
  dyRangeSelector() %>% dyEvent("2015-6-16", "announced candidacy", labelLoc = "bottom") %>%
  dyEvent("2016-7-19", "became the nominee", labelLoc = "bottom") %>%
  dyEvent("2016-11-8", "won the election", labelLoc = "bottom")

```

**Figure 2: Trump's Twitter follower counts by day**



# Section II: Decomposing Trump's Twitter followers

Data comes from Song, who did an amazing job at harvesting data and creating and computing Trump followers' statistics.

We divided the time into three periods: pre-announcement, primary, and general election. He sampled from Trump's first 13 million followers (until 11/08/2016) weighted by their follower sizes --  

**124,959 followers from roughly his first 3 million (pre-announcement);** 

**191,811 followers from his 3 tp 9.8 million followers (primary election);** 

**60,955 from his 9.8 to 13 million followers (general election).** 


For each set of followers, we cluserted them into 50 clusters **based on who follows who**, resulting in 150 clusters from all three periods. 

Each cluster was interpreted based on the top 40 accounts people followed, people's region, language, and their follower and following counts.

Notes on follower and following counts interpretations: 

*influencers: number of followers greatly outweighs number of following

*online marketers: number of followers is large and similar to number of following (bio: marketer, inspirational speaker, entreprenuer, etc.)

*popular/followback accounts: number of followers is large and similar to number of following

*popular grassroots: number of followers is large and a bit larger than number of following


```{r include=FALSE}
####read clusters
df = read.csv("Trump_clusters_4_24.csv")
unique(df$cluster_label)
df = df %>% mutate(cluster_cat = ifelse( cluster_label == "South Africa" | cluster_label == "Nigeria" | cluster_label == "Venezuela" | cluster_label == "British" |cluster_label == "Australia" | cluster_label == "Kenya" | cluster_label == "Mongolia" | cluster_label == "Canada" | cluster_label == "France" | cluster_label == "mixed" | cluster_label == "Netherlands"| cluster_label == "India"| cluster_label == "Brazilian"| cluster_label == "Nepal"| cluster_label == "Denmark"| cluster_label == "AZ, Tokyo, Turkey"| cluster_label == "Russia"| cluster_label == "Mexico", "other countries", as.character(cluster_label)))
#reorder period
df$period = factor(df$period, levels = c("pre announcement", "primary election", "general election"))

df$cluster_cat1[df$cluster_cat == "Trump supporters"] = "Trump supporters"
df$cluster_cat1[df$cluster_cat == "conservatives"] = "conservatives"
df$cluster_cat1[df$cluster_cat == "anti-feminist conservatives"] = "anti-feminist conservatives"
df$cluster_cat1[df$cluster_cat == "religious"] = "conservatives"
df$cluster_cat1[df$cluster_cat == "NRA members"] = "conservatives"
df$cluster_cat1[df$cluster_cat == "news junkies"] = "news&regional"
df$cluster_cat1[df$cluster_cat == "journalists"] = "news&regional"
df$cluster_cat1[df$cluster_cat == "Miami"] = "news&regional"
df$cluster_cat1[df$cluster_cat == "California tech scene"] = "news&regional"
df$cluster_cat1[df$cluster_cat == "liberals"] = "liberals"
df$cluster_cat1[df$cluster_cat == "far left"] = "liberals"
df$cluster_cat1[df$cluster_cat == "non-political"] = "non-political"
df$cluster_cat1[df$cluster_cat == "other countries"] = "other countries"
df$cluster_cat1[df$cluster_cat == "international"] = "international"

df$cluster_cat1 = factor(df$cluster_cat1, levels = c("Trump supporters", "anti-feminist conservatives", "conservatives", "liberals", "news&regional", "international", "non-political", "other countries"))

```

### 2.1 The composition of followers in each period

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
df %>% group_by(period, cluster_cat1) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = cluster_cat1, label = cluster_cat1)) +
  geom_bar(stat = "identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")
```

**Figure 3: Distribution of 150 clusters by cluster number in three periods**


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
df %>% group_by(period, cluster_cat1) %>% summarise(count = sum(clust_size)) %>% ggplot(aes(x = period, y = count, fill = cluster_cat1, label = cluster_cat1)) +
  geom_bar(stat = "identity" ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")
```

**Figure 4.1: Distribution of of 150 clusters by cluster size in three periods**

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
df %>% group_by(period, cluster_cat1) %>% summarise(count = sum(clust_size)) %>% ggplot(aes(x = period, y = count, fill = cluster_cat1)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_fill_brewer(palette="Spectral") 
```

**Figure 4.2: Distribution of of 150 clusters by percentage in three periods**



### 2.2 Following time

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 10, fig.height=6}
df$time_order_150 = rank(df$time_order.million)

df %>% ggplot(aes(x = time_order_150, y = clust_size, fill = cluster_cat1)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette="Spectral")
```

**Figure 5: Plot cluster categories against time by cluster size**


```{r include=FALSE, warning=FALSE, message=FALSE}
#######read followers
# classes =  c("numeric", "character", "character", "character", "character", "factor", "character", "character", "character", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric")
fg = read.csv("followers_info_general.csv", header = TRUE, sep = ",")
fg$period = rep("general election", length(fg$id_str)) 
fpri = read.csv("followers_info_primary.csv", header = TRUE, sep = ",")
fpri$period = rep("primary election", length(fpri$id_str)) 
fpre = read.csv("followers_info_pre.csv", header = TRUE, sep = ",")
fpre$period = rep("pre announcement", length(fpre$id_str)) 
fpre$id_str = as.character(fpre$id_str)
fpri$id_str = as.character(fpri$id_str)
fg$id_str = as.character(fg$id_str)

f_all = rbind (fg %>% select(id_str, favourites_count:period), fpri %>% select(id_str, favourites_count:period), fpre %>% select(id_str, favourites_count:period))
#people who don't have a cluster ID: 55264, an ID has to follow at least 10 people to be in the clustering
sum(is.na(f_all$cluster))

#merge with cluster information: by cluster id and period
df_sub = df %>% select(period, cluster_id, cluster_label, label_note, cluster_cat1, time_order_150)
colnames(f_all)[8] <- 'cluster_id'
f_all$period = as.factor(f_all$period)
f_all$period = factor(f_all$period, levels = c("pre announcement", "primary election", "general election"))
f_final = left_join((f_all %>% filter(!is.na(cluster_id))), df_sub)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 12, fig.height=6}
f_final %>% ggplot(aes(x = factor(time_order_150), y = time_order, fill = cluster_cat1)) + geom_boxplot() + stat_summary(fun.y = mean, geom="point",colour="darkred", size=1) +
  scale_fill_brewer(palette="Spectral") + theme(axis.text.x = element_text(angle = 30, hjust = 1))

```
**Figure 6: Distribution of time ids**

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 10, fig.height=6}
f_final %>% mutate(million = time_order%/%100000+1) %>% group_by(million, cluster_cat1) %>% summarise(count = n()) %>% ggplot(aes(x = factor(million), y = count, fill = cluster_cat1)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_fill_brewer(palette="Spectral") + 
  geom_vline(xintercept = 30) + geom_text(aes(30,0,label = "announced candidacy", vjust = 1)) +
  geom_vline(xintercept = 98) + geom_text(aes(98,0,label = "became the nominee", vjust = 1))

```

**Figure 7: Composition of followers by 100k**


### 2.3 Compare features of cluster size, time, follower/following/favourite/status/retweet counts


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
#boxplot for each cluster category's clustersize, retweet count, ratio 
df %>% ggplot(aes(x = cluster_cat1, y = clust_size, fill = factor(period))) + geom_boxplot() + stat_summary(fun.y = mean, geom="point",colour="darkred",size=2,
    position=position_dodge(width=0.75)) + theme(axis.text.x = element_text(angle = 50, hjust = 1))

f_final %>% ggplot(aes(x = cluster_cat1, y = time_order, fill = factor(cluster_cat1))) + geom_boxplot() + stat_summary(fun.y = mean, geom="point",colour="darkred",size=2, position=position_dodge(width=0.75)) + theme(axis.text.x = element_text(angle = 50, hjust = 1), legend.position = "none")
```

**Figure 8: Compare cluster size and time order**



```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 12, fig.height=8}
f_final %>% gather(`followers_count`, `friends_count`, `statuses_count`, `favourites_count`, key = "metric", value = "count") %>% ggplot(aes(x = cluster_cat1, y = log(count), fill = factor(cluster_cat1))) + geom_boxplot() + stat_summary(fun.y = mean, geom="point",colour="darkred",size=2, position=position_dodge(width=0.75)) + theme(axis.text.x = element_text(angle = 50, hjust = 1), legend.position = "none") + facet_wrap(~metric, nrow = 2)

```

**Figure 9: Compare follower/following/favourite/status counts**



```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 12, fig.height=8}

f_final %>% ggplot(aes(x = cluster_cat1, y = retweet_trump, fill = factor(period))) + stat_summary(fun.y = mean, geom="point",colour="darkred",size=3, position=position_dodge(width=0.75)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 50, hjust = 1)) + scale_fill_discrete(name = "Time period") + ylab("Each follower's retweeting times")

f_final %>% group_by(cluster_cat1) %>% summarise(retweet_total = sum(retweet_trump, na.rm = TRUE), num_people = n()) %>% mutate(retweet_per_person = retweet_total/num_people) %>% ggplot(aes(x = cluster_cat1, y = retweet_per_person, fill = cluster_cat1)) + geom_bar(stat = "identity") + ylab("Average retweeting times") + theme(legend.position = "none")

df %>% ggplot(aes(x = cluster_cat1, y = retweet.ratio)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 50, hjust = 1)) + ylab("Percentage of followers who retweeted Trump")

```

**Figure 10: Comparing retweets by three measures**


# Section III: Explore Retweet Patterns of the Clusters

### 3.1 Retweet counts of each cluster category over time

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 10, fig.height=6}
temp = df %>% select(cluster_cat1, clust_size, Y.2015.01:Y.2016.11) %>% gather(`Y.2015.01`:`Y.2016.11`, key = month, value = tweet_count) %>% group_by(cluster_cat1, month) %>% summarise(ave_tweet_count_weighted_by_cluster_size = mean(tweet_count/clust_size)) %>% mutate(date = as.Date(paste(substr(month, 3,9), ".15", sep = ""), format = "%Y.%m.%d"))

temp %>% ggplot(aes(x = date, y = ave_tweet_count_weighted_by_cluster_size, color = cluster_cat1)) + geom_line() + geom_point(size = 2)

```
**Figure 11 : Monthly retweet pattern of each cluster category**


### 3.2 What were people retweeting in each cluster category?

First, we used topic modeling to extract several themes of Trumps tweets. We found that his tweets ranged from criticisms and attacks to standard campaign rhetoric. Each of Trump's tweets was assigned a topic label.

Then, we explored what kind of tweets each cluster category was retweeting. 

What tweets was each cluster category retweeting from Trump?

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width= 10, fig.height=6}
followers_complete = read.csv("followers_with_cluster_info.csv")

f1 = followers_complete %>% gather(`campaign.slogan`:`via_at`, key = "topic", value = "count") %>% group_by(cluster_label, topic) %>% summarise(per_follower_count = mean(count))

f1$topic[f1$topic == "announce.media.presence.1"] = "announce.media.presence"
f1$topic[f1$topic == "announce.media.presence.2"] = "announce.media.presence"
f1$topic[f1$topic == "announce.media.presence.and.crticize.media"] = "announce.media.presence"
f1$topic[f1$topic == "call.for.support"] = "call.for.support.vote"
f1$topic[f1$topic == "call.for.vote"] = "call.for.support.vote"
f1$topic[f1$topic == "call.for.vote.1"] = "call.for.support.vote"
f1$topic[f1$topic == "campaign.slogan.1"] = "campaign.slogan"
f1$topic[f1$topic == "campaign.slogan.2"] = "campaign.slogan"
f1$topic[f1$topic == "criticize.opponents.1"] = "criticize.opponents"
f1$topic[f1$topic == "criticize.opponents.2"] = "criticize.opponents"
f1$topic[f1$topic == "criticize.opponents.3"] = "criticize.opponents"
f1$topic[f1$topic == "praise.surrogates.1"] = "praise.surrogates"
f1$topic[f1$topic == "thank_you"] = "express.appreciation"
f1$topic[f1$topic == "express.appreciation.1"] = "express.appreciation"
f1$topic[f1$topic == "via_at"] = "retweet_endorse"
f1$topic[f1$topic == "cite.positive.news"] = "retweet_endorse"
f1$topic[f1$topic == "campaign.stops.1"] = "campaign.stops"
f1$topic[f1$topic == "campaign.stops"] = "campaign.tweets"
f1$topic[f1$topic == "campaign.slogan"] = "campaign.tweets"
f1$topic[f1$topic == "call.for.support.vote"] = "campaign.tweets"
f1$topic[f1$topic == "express.appreciation"] = "campaign.tweets"
f1$topic[f1$topic == "join_us"] = "campaign.tweets"
f1$topic[f1$topic == "announce.media.presence"] = "campaign.tweets"



f1 %>% ggplot(aes(x = cluster_label, y = per_follower_count, fill = topic)) + geom_bar(stat = "identity", position = "fill") + theme(axis.text.x = element_text(angle = 50, hjust = 1))

```


# Section IV: BOTS

### How do we define bots?

1) weekly count of tweets (results will be out soon)

2) follower/following/favourite/status/retweet counts

```{r echo=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
f_final %>% filter(followers_count <= 100) %>% ggplot(aes(x = factor(followers_count), y = friends_count)) + geom_boxplot()
f_final %>% filter(followers_count <= 100) %>% ggplot(aes(x = factor(followers_count), y = favourites_count)) + geom_boxplot()
f_final %>% filter(followers_count <= 100) %>% ggplot(aes(x = factor(followers_count), y = statuses_count)) + geom_boxplot()
f_final %>% filter(followers_count <= 100) %>% ggplot(aes(x = factor(followers_count), y = retweet_trump)) + geom_boxplot()
```

Experimenting with parameters: 

following_follower = friends_count/followers_count

bots: following_follower > 50, followers_count < 50

```{r echo=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
#by raw counts
f_final %>% mutate (following_follower = friends_count/followers_count) %>% filter (following_follower > 50, followers_count < 50) %>% 
  group_by(period, cluster_cat1) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = cluster_cat1, label = cluster_cat1)) +
  geom_bar(stat = "identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")

#by percentage
f_final %>% mutate (following_follower = friends_count/followers_count) %>% filter (following_follower > 50, followers_count < 50) %>% 
  group_by(period, cluster_cat1) %>% summarise(count = n()) %>% ggplot(aes(x = period, y = count, fill = cluster_cat1, label = cluster_cat1)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_fill_brewer(palette="Spectral") 


```


### Clustering Trump followers using follower/following/favourite/status/retweet counts

```{r echo=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
f_final$retweet_trump[is.na(f_final$retweet_trump)] = 0
a = f_final %>% select (id_str, cluster_cat1, followers_count, friends_count, statuses_count, favourites_count, retweet_trump)

wss <- (nrow(a)-1)*sum(apply(a[, -c(1, 2)],2,var))
for (i in 2:9) wss[i] <- sum(kmeans(a[, -c(1, 2)], centers=i)$withinss)
plot(1:9, wss, type="b", xlab="Number of Clusters",
     ylab="Within groups sum of squares")
```

```{r}
set.seed(7)
K = 6
km = kmeans(a[, -c(1, 2)], K, nstart = 10)
table(km$cluster)
```

```{r echo=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width= 8, fig.height=6}
kmd = as.data.frame(list(cluster = a$cluster_cat1, follower_count = a$followers_count, following_count = a$friends_count, fav_count = a$favourites_count, status_count = a$statuses_count, rt_count = a$retweet_trump, value = as.factor(km$cluster)))

kmd %>% gather(`follower_count`: `rt_count`, key = "measure", value = "count") %>% group_by(value, measure) %>% summarise(log_mean = log(mean(count))) %>% ggplot(aes(x = factor(value), y = log_mean, fill = measure )) + geom_bar(stat = "identity") + scale_color_brewer(palette = "Set2")

kmd %>% ggplot(aes(cluster, fill = factor(value))) + geom_bar(position = "fill")
```

